---
title: "COBIND 2022 results"
author: Ieva Rauluseviciute
email : ievarau@uio.no
github : ievarau
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  # html_document:
  #   keep_md: yes
  md_document:
    variant: gfm
has_children: true
---

```{r setup-options, cache = TRUE, echo = FALSE, eval = TRUE, include = FALSE}

required.libraries <- c("tidyverse")

for (lib in required.libraries) {
  suppressPackageStartupMessages(library(lib, character.only = TRUE, quietly = T))
}

options(stringsAsFactors = FALSE)
```

**COBIND** pipeline aims to identify the co-binders/co-factors of transcription factors (TFs). The method uses coordinates of transcription factor binding sites (TFBSs) as an input and returns information about co-binders and their binding fashion — spacings between the two binding sites.

The code that was used to produce COBIND 2022 results is stored in this [repository](https://bitbucket.org/CBGR/pipeline_cobind/src/master/). COBIND pipeline is also as a tool and can be found in this [repository](https://bitbucket.org/CBGR/cobind_tool/src/master/).


## What to expect from this page? ##

This page contains results from COBIND 2022 analysis. We analysed 8,792 datasets of high-confidence TFBSs stored in [UniBind 2021](https://unibind.uio.no/) database for 404 unique TFs that collectively are from 7 species: _Arabidopsis thaliana_, _Caenorhabditis elegans_, _Danio rerio_, _Drosophila melanogaster_, _Homo sapiens_, _Mus musculus_ and _Rattus norvegicus_.


Reports about discovered co-binders are provided for each TF (where at least one co-binder was discovered) in different species. Another group of reports report the discovered co-binders summarized over TF families. Conservation summaries are available for all species, except  _Danio rerio_ and _Rattus norvegicus_.

# Species-specific results

```{r individual_families_reports, cache = TRUE, echo = FALSE, eval = TRUE, include = TRUE, results = 'asis'}

##----------------##
## Species labels ##
##----------------##

## Species table:
species_tab           <- as.data.frame(cbind(c("ARABIDOPSIS", "CELEGANS", "DRERIO",
                                               "DROSOPHILA", "HUMAN", "MOUSE", "RAT"),
                                             c("Arabidopsis thaliana", "Caenorhabditis elegans", "Danio rerio", 
                                               "Drosophila melanogaster", "Homo sapiens", "Mus musculus", "Rattus norvegicus"),
                                             c("ARABIDOPSIS.png", "CELEGANS.png", "DRERIO.png",
                                               "DROSOPHILA.png", "HUMAN.png", "MOUSE.png", "RAT.png")))
colnames(species_tab) <- c("species_ID", "species_name", "icon_path")

##-------------##
## Directories ##
##-------------##

icons.dir             <- "images/species_icons"

## Individual:
individual_results_dir          <- "COBIND_results/individual"
list.of.species.dirs.individual <- list.dirs(individual_results_dir, recursive = FALSE)

## Families:
families_results_dir            <- "COBIND_results/families"
list.of.species.dirs.families   <- list.dirs(families_results_dir, recursive = FALSE)

##---------------------##
## Listing the reports ##
##---------------------##

for (species.dir in list.of.species.dirs.individual) {
  
  ## Families dir:
  families.species.dir     <- gsub(species.dir, 
                                   pattern = "\\/individual\\/", 
                                   replacement = "\\/families\\/")
  
  ## Species name:
  species_thr       <- basename(species.dir)
  species_name_ID   <- unlist(strsplit(species_thr, "_"))[1]
  species_name      <- species_tab %>%
                        dplyr::filter(species_ID == species_name_ID) %>%
                        dplyr::select(species_name, icon_path)
  
  species_icon_path <- file.path(icons.dir, species_name$icon_path)
  species_name      <- species_name$species_name
  
  cat(paste0("## **", species_name, "**"))
  cat(paste0("\n<img src='",
             species_icon_path,
             "' class='img-responsive' alt='' height = '100px'>\n"))
  cat("\n\n")

  ##------------##
  ## Individual ##
  ##------------##
  ## Listing all available reports:
  list.of.individual.reports <- list.files(species.dir,
                                           pattern = ".html",
                                           recursive = TRUE,
                                           full.names = TRUE)
  
  cat("<details markdown='1'>")
  cat("\t<summary><b>Results for individual TFs</b></summary>\n<br>\n")
  
  for (report.path in list.of.individual.reports) {

    tf_name <- basename(dirname(report.path))

    cat(paste0("<p><a href='", report.path, 
               "'>",
               tf_name,
               "</a></p>"))

  }
  
  cat("</details>\n\n")
  
  ##----------##
  ## Families ##
  ##----------##
  ## Listing all available reports:
  list.of.families.reports <- list.files(families.species.dir,
                                         pattern = ".html",
                                         recursive = TRUE,
                                         full.names = TRUE)
  
  cat("<details markdown='1'>")
  cat("\t<summary><b>Results for TF families</b></summary>\n<br>\n")
  
  for (report.path in list.of.families.reports) {

    tf_name <- basename(dirname(report.path))

    cat(paste0("<p><a href='", report.path, 
               "'>",
               tf_name,
               "</a></p>"))
  }
  
  ##------------------------##
  ## Conservation summaries ##
  ##------------------------##
  
  ## Adding conservation summaries for certain species:
  if (species_name_ID != "RAT" & species_name_ID != "DRERIO") {
    
    cat("</details>\n\n")
    
    ## Individual:
    individual.top.conservation.path <- file.path(species.dir, "all_pvalues_conservation.png")
    individual.all.conservation.path <- file.path(species.dir, "top_conserved_cobinders_pvalues_conservation.png")
    
    cat("<details markdown='1'>")
    cat("\t<summary><b>Conservation summaries from individual TFs analysis</b></summary>\n<br>\n")

    cat(paste0("\n<img src='",
               individual.all.conservation.path,
             "' class='img-responsive' alt='' height = '300px'>\n\n"))
    cat("**Distribution of conservation p-values for all co-binders**\n<br>\n")
    
    cat(paste0("\n<img src='",
               individual.top.conservation.path,
             "' class='img-responsive' alt='' height = '300px'>\n\n"))
    cat("**Distribution of conservation p-values for top most conserved co-binders**\n<br>\n")
    
    cat("</details>\n\n")
  
    ## Families:
    families.top.conservation.path <- file.path(families.species.dir, "all_pvalues_conservation.png")
    families.all.conservation.path <- file.path(families.species.dir, "top_conserved_cobinders_pvalues_conservation.png")
    
    cat("<details markdown='1'>")
    cat("\t<summary><b>Conservation summaries from TF families analysis</b></summary>\n<br>\n")

    cat("**Distribution of conservation p-values for all co-binders**\n<br>\n")
    cat(paste0("\n<img src='",
               families.all.conservation.path,
               "' class='img-responsive' alt='' height = '300px'>\n\n"))
    
    cat("**Distribution of conservation p-values for top most conserved co-binders**\n\n")
    cat(paste0("\n<img src='",
               families.top.conservation.path,
               "' class='img-responsive' alt='' height = '300px'>\n<br>\n"))
    
    cat("</details>\n<br>\n")
    cat("<br>\n")
    cat("\n")
    
  } else {
    
    cat("</details>\n\n")
    cat("<br>\n")
    cat("\n")
    
  }

}

```

# Interspecies results #


```{r interspecies_reports, cache = TRUE, echo = FALSE, eval = TRUE, include = TRUE, results = 'asis'}

##-------------##
## Directories ##
##-------------##

interspecies_results_dir          <- "COBIND_results/interspecies"

##---------------------##
## Listing the reports ##
##---------------------##

##------------##
## Individual ##
##------------##

interspecies.individual.dir  <- file.path(interspecies_results_dir, "individual_0.99")

list.of.interspecies.individual.reports <- list.files(interspecies.individual.dir,
                                           pattern = ".html",
                                           recursive = TRUE,
                                           full.names = TRUE)
  
cat("<details markdown='1'>")
cat("\t<summary><b>Results for individual TFs</b></summary>\n<br>\n")
  
for (report.path in list.of.interspecies.individual.reports) {

  tf_name <- basename(dirname(report.path))

  cat(paste0("<p><a href='", report.path, 
             "'>",
               tf_name,
             "</a></p>"))

  }
  
cat("</details>\n\n")

##----------##
## Families ##
##----------##

interspecies.families.dir  <- file.path(interspecies_results_dir, "families_0.99")

list.of.families.individual.reports <- list.files(interspecies.families.dir,
                                           pattern = ".html",
                                           recursive = TRUE,
                                           full.names = TRUE)
  
cat("<details markdown='1'>")
cat("\t<summary><b>Results for TF families</b></summary>\n<br>\n")
  
for (report.path in list.of.families.individual.reports) {

  tf_name <- basename(dirname(report.path))

  cat(paste0("<p><a href='", report.path, 
             "'>",
               tf_name,
             "</a></p>"))

  }
  
cat("</details>\n<br>\n")


```

## Protein-protein interaction (PPI) analysis summary ##


```{r ppi_summary, cache = TRUE, echo = FALSE, eval = TRUE, include = TRUE, results = 'asis'}

##-------------##
## Directories ##
##-------------##

interspecies_results_dir              <- "COBIND_results/interspecies"

interspecies.individual.dir           <- file.path(interspecies_results_dir, "individual_0.99")

individual.specific.ppi.summary.path  <- file.path(interspecies.individual.dir,
                                          "ppi_summary_individual_species_library.png")
individual.ppi.summary.path           <- file.path(interspecies.individual.dir,
                                          "ppi_summary_individual_full_library.png")
  
cat("Numbers of co-binders are summarized in the barplot and reflect the number of anchor-co-binder pairs in different species that had significant motif similarity match in motif libraries, which then was found in the protein-protein data with a significant combined score. \n<br>\n<br>\n<br>\n")

cat("<details markdown='1'>")
cat("\t<summary><b>See summary plot when compared to species-specific motif libraries</b></summary>\n<br>\n")
  
cat(paste0("\n<img src='",
               individual.specific.ppi.summary.path,
               "' class='img-responsive' alt='' height = '300px'>\n"))

cat("</details>\n<br>\n")
cat("\n")

cat("<details markdown='1'>")
cat("\t<summary><b>See summary plot when compared to full motif library</b></summary>\n<br>\n")
  
cat(paste0("\n<img src='",
               individual.ppi.summary.path,
               "' class='img-responsive' alt='' height = '300px'>\n"))

cat("</details>\n<br>\n")
cat("<br>\n")
cat("\n")


```

# Species icons sources #

Species icons were taken from:

* [ _Arabidopsis thaliana_ ](http://www.namethatplant.net/plantdetail.shtml?plant=3236)
* [ _Caenorhabditis elegans_ ](https://commons.wikimedia.org/wiki/File:Nematode_%28Caenorhabditis_elegans%29.png)
* [ _Danio rerio_ ](https://commons.wikimedia.org/wiki/File:Zebrafish.png)
* [ _Drosophila melanogaster_](https://commons.wikimedia.org/wiki/File:Drosm3.svg)
* [ _Homo sapiens_ ](https://freesvg.org/ancient-greek-short-hairstyle-vector-illustration11883)
* [ _Mus musculus_ ](https://freesvg.org/vector-graphics-of-mouse-with-long-tail)
* [ _Rattus norvegicus_ ](https://freesvg.org/1547508146)







