---
title: "COBIND 2022 results"
author: Ieva Rauluseviciute
email : ievarau@uio.no
github : ievarau
date: July 22, 2022
output:
  md_document:
    variant: gfm
has_children: true
---

```{r setup-options, cache = TRUE, echo = FALSE, eval = TRUE, include = FALSE}

required.libraries <- c("tidyverse")

for (lib in required.libraries) {
  suppressPackageStartupMessages(library(lib, character.only = TRUE, quietly = T))
}
```

**COBIND** pipeline aims to identify the co-binders/co-factors of transcription factors (TFs). The method uses coordinates of transcription factor binding sites (TFBSs) as an input and returns information about co-binders and their binding fashion — spacings between the two binding sites.

This repository and its contents were used to produce the results for the COBIND manuscript. We made available COBIND as a tool, which can be found [here](https://bitbucket.org/CBGR/cobind_tool/src/master/).


## What to expect from this page? ##

This page contains results from COBIND 2022 analysis. We analysed 8,792 datasets of high-confidence TFBSs stored in [UniBind 2021](https://unibind.uio.no/) database for 404 unique TFs that collectively are from 7 species: _Arabidopsis thaliana_, _Caenorhabditis elegans_, _Danio rerio_, _Drosophila melanogaster_, _Homo sapiens_, _Mus musculus_ and _Rattus norvegicus_.


Reports about discovered co-binders are provided for each TF (where at least one co-binder was discovered) in different species. Another group of reports report the discovered co-binders summarized over TF families.

# Results #

## Individual transcription factors ##

```{r individual_reports, cache = TRUE, echo = FALSE, eval = TRUE, include = TRUE, results = 'asis'}

## Species table:
species_tab           <- as.data.frame(cbind(c("ARABIDOPSIS", "CELEGANS", "DRERIO",
                                               "DROSOPHILA", "HUMAN", "MOUSE", "RAT"),
                                             c("Arabidopsis thaliana", "Caenorhabditis elegans", "Danio rerio", 
                                               "Drosophila melanogaster", "Homo sapiens", "Mus musculus", "Rattus norvegicus"),
                                             c("ARABIDOPSIS.png", "CELEGANS.png", "DRERIO.png",
                                               "DROSOPHILA.png", "HUMAN.png", "MOUSE.png", "RAT.png")))
colnames(species_tab) <- c("species_ID", "species_name", "icon_path")

## Directories:
icons.dir             <- "images/species_icons"
results_dir           <- "COBIND_results/individual"
list.of.species.dirs  <- list.dirs(results_dir, recursive = FALSE)

## Creating reports lists:
for (species.dir in list.of.species.dirs) {
  
  species_thr     <- basename(species.dir)
  species_name_ID <- unlist(strsplit(species_thr, "_"))[1]
  species_name    <- species_tab %>%
                      dplyr::filter(species_ID == species_name_ID) %>%
                      dplyr::select(species_name, icon_path)
  
  species_icon_path <- file.path(icons.dir, species_name$icon_path)
  species_name      <- species_name$species_name
  
  ## Listing all available reports:
  list.of.reports   <- list.files(species.dir,
                                  pattern = ".html",
                                  recursive = TRUE,
                                  full.names = TRUE)
  cat("<picture>")
  # cat(paste0("\n<br/>\n <img src=./",
  #            species_icon_path,
  #            " height = '30px'></img> \n<br/>\n "))
  # cat("</picture>")
  cat(paste0(" ### **", species_name, "** ### \n<br/>\n"))
  
  cat("<details>  \n")
  cat("\t<summary><b> Click to access results for each TF. </b></summary>  \n<br/>\n")
  
  cat("<p>")
  cat("\n\t")
  
  for (report.path in list.of.reports) {
    
    tf_name <- basename(dirname(report.path))
    
    cat(paste0(" \t * [", tf_name, "](", report.path,")\n"))

  }
  cat("</p>")
  
  cat("<br/></details>  \n<br/>\n")
}

cat("<br/>")
cat("\n")
cat("\n")
```




## Transcription factor families ##


### References ###

Species icons were taken from:

* [ _Arabidopsis thaliana_ ](http://www.namethatplant.net/plantdetail.shtml?plant=3236)
* [ _Caenorhabditis elegans_ ](https://commons.wikimedia.org/wiki/File:Nematode_%28Caenorhabditis_elegans%29.png)
* [ _Danio rerio_ ](https://commons.wikimedia.org/wiki/File:Zebrafish.png)
* [ _Drosophila melanogaster_](https://commons.wikimedia.org/wiki/File:Drosm3.svg)
* [ _Homo sapiens_ ](https://freesvg.org/ancient-greek-short-hairstyle-vector-illustration11883)
* [ _Mus musculus_ ](https://freesvg.org/vector-graphics-of-mouse-with-long-tail)
* [ _Rattus norvegicus_ ](https://freesvg.org/1547508146)







